\cvsection{Employment}

\cvevent{Research Scientist}{Arizona State University}{Dec 2013 -- Aug
  2015}{}

\textit{Supervisor: Dr. Mikhail Chester}

\vspace{6pt}

\begin{itemize}
\item Full-time researcher for the \textit{Sustainable Urban Systems Lab}.
\item Performed research in life-cycle assessment, climate modeling, hydrologic
  modeling, and risk analysis.
\item Authored and published three articles in high-impact journals.
\end{itemize}

\divider

\cvevent{Lab Assistant}{SILC Learning Support Services}{June 2008 -- Jan
  2013}{}

\textit{Supervisor: Dr. Andrew Ross}

\vspace{6pt}

\begin{itemize}
\item Provided technical assistance to students in the \textit{School of
    International Letters and Cultures} at Arizona State University.
\end{itemize}

\cvsection{Software}

\cvachievement{\faGlobe}{pysheds}{Simple and fast watershed delineation in
  python.
  
  \vspace{6pt}

  \begin{tabular}{l l l}
  \faStar \ \ 186 \ \ \ \ \ & \faCodeFork \ \ 57 \ \ \ \ \ & \faEye \ \ 14 
  \end{tabular}
  
  \vspace{6pt}
  \small Available at:
  \texttt{github.com/mdbartos/pysheds}
}

\divider

\cvachievement{\faTree}{rrcf}{Implementation of the \textit{Robust Random Cut
  Forest} algorithm for anomaly detection on streams.

  \vspace{6pt}

  \begin{tabular}{l l l}
  \faStar \ \ 111 \ \ \ \ \ & \faCodeFork \ \ 37 \ \ \ \ \ & \faEye \ \ 11
  \end{tabular}

  \vspace{6pt}
  \small Available at:

  \texttt{github.com/kLabUM/rrcf}
}

\divider

\cvachievement{\faBug}{perfect-cell}{General purpose firmware for cell-enabled
  PSoC motes.

  \vspace{6pt}

  \begin{tabular}{l l l}
  \faStar \ \ 12 \ \ \ \ \ & \faCodeFork \ \ 8 \ \ \ \ \ & \faEye \ \ 5
  \end{tabular}

  
  \vspace{6pt}
  \small Available at:
  \texttt{github.com/open-storm/perfect-cell}
}

\divider

\cvachievement{\faTint}{superlink}{Implementation of the SUPERLINK hydraulic
  solver.

  \vspace{6pt}

  \begin{tabular}{l l l}
  \faStar \ \ 4 \ \ \ \ \ & \faCodeFork \ \ 1 \ \ \ \ \ & \faEye \ \ 1
  \end{tabular}

  \vspace{6pt}
  \small Available at:
  \texttt{github.com/mdbartos/superlink}
}
